Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-01-10 DingHickKritzMakRICAMChap.tex
update

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

@@

@@

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Kritzer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{...}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{...}
  \affil[4]{...}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  \subtitle{...}
  \abstract{...}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

Adaptive algorithms may perform better in the set of input functions is not convex, and that is the situation studied here. We propose adaptive algorithms for general multivariate linear problems where the input function lies in a non-convex cone.  Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.  We show our algorithms to be essentially optimal.  We derive conditions under which the problem is tractable.  In the remainder of this section we define the problem and essential notation.

@@

\begin{lemma} \label{DHKM:Key_Lem}
Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined by the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{equation*}
\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
\end{lemma}
\begin{proof}
The proof proceeds by applying H\"older's inequality
\begin{align}
    \label{DHKM:SOL_A}
    \norm[\calG]{\SOL(f)}  
    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
\nonumber
    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
    \nonumber
    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
\end{align}
which establishes inequality \eqref{DHKM:SOL_ineq}.
Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \norm[\calG]{\SOL(f)}  
    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
\end{equation*}
Moreover,
\begin{equation*}
    \norm[\calF]{f}  
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof}

@@

The $\lambda_{\bsk}$ define the smoothness of the input space and have a known order:
\begin{equation} \label{DHKM:lambda_order}
    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots.
\end{equation}
An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk) v_{\bsk}, \quad \APP(f,0) = 0.
\end{equation}

@@

\FredNote{Peter please add here.}

@@

@@

\begin{theorem}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
\begin{equation} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \varepsilon/(\frakC R) \right \}.
\end{equation}
The computational complexity has the lower bound
\begin{equation} \label{DHKM:PilotConeAlg_comp}
        \COMP(\calA(\calC),\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
\end{equation}
\end{theorem}

\begin{proof} \FredNote{Fred is working on this proof.}
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \},  
\end{align*}
since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le \norm[\calF]{f} \le R$ for all $f \in \calB_R$.  Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.   Fix $R$ and $\varepsilon$ arbitarily.  Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.  Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.

@@

Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
=\frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
& \ge \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
\end{align*}
by the ordering of the $\bsk_i$.  This inequality implies complexity bound \eqref{DHKM:PilotConeAlg_comp}.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{
.0
.
.} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{The work with Simon}

\begin{acknowledgement}
  ...
\end{acknowledgement}

>>>>

\usepackage[notref,notcite]{showkeys}

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

@@

\allowdisplaybreaks

@@

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Kritzer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{...}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{Johann Radon Institute for Computational and Applied Mathematics (RICAM), 
  Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
  \affil[4]{...}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  \subtitle{...}
  \abstract{...}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

Adaptive algorithms may perform better if the set of input functions is not convex, and that is the situation studied here. We propose adaptive algorithms for general multivariate linear problems where the input function lies in a non-convex cone.  Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.  We show our algorithms to be essentially optimal.  We derive conditions under which the problem is tractable.  In the remainder of this section we define the problem and essential notation.

@@

\begin{lemma} \label{DHKM:Key_Lem}
Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined by the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{equation*}
\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
\PeterNote{Should not $\rho'$ be 2 in the Ding et al. case?}

Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
\end{lemma}
\begin{proof}
The proof proceeds by applying H\"older's inequality
\begin{align}
    \label{DHKM:SOL_A}
    \norm[\calG]{\SOL(f)}  
    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
\nonumber
    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
    \nonumber
    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
\end{align}
which establishes inequality \eqref{DHKM:SOL_ineq}.
Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \norm[\calG]{\SOL(f)}  
    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
\end{equation*}
Moreover,
\begin{equation*}
    \norm[\calF]{f}  
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof}

@@

The $\lambda_{\bsk}$ define the smoothness of the input space and have a known order:
\begin{equation} \label{DHKM:lambda_order}
    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots.
\end{equation}
An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i}, \quad \APP(f,0) = 0.
\end{equation}

@@

\PeterNote{Why do we need the product structure?}

\FredNote{If we don't need it then, let's not introduce it.  But I think that at some point we may want it.}

\PeterNote{I agree.}

\PeterNote{started working on general tractability notions here.

\bigskip

We would like to study how $\COMP(\calA(\calC), \varepsilon,R)$ 
depends on the dimension $d$ and the error threshold $\varepsilon$. This is described by defining various notions of tractability. Roughly speaking, the different tractability notions correspond to different 
ways of how the complexity $\COMP(\calA(\calC), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent 
to the problem, not to a particular algorithm. 
We define the following notions of tractability (for further information on tractability we refer to the trilogy 
\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}).

\begin{itemize}   
\item We say that the adaptive approximation problem is strongly polynomially tractable
if and only if there are non-negative $C$ and $p$ such that   
for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
$$   
\COMP(\calA(\calC), \varepsilon,R)\le C\,\varepsilon^{-p}.
$$   
The infimum of $p$ satisfying the bound above is denoted by $p^*$   
and is called the exponent of strong polynomial tractability.    
\newline \qquad

\item    
We say that the problem is polynomially tractable
if and only if there are non-negative $C,p$, and $q$ such that   
for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
$$   
\COMP(\calA(\calC), \varepsilon,R)\le C\,d^{\,q}\,   
\varepsilon^{-p}.   
$$   
\vskip 0.5pc     
\item   
We say that the problem is quasi-polynomially tractable if and only if there are non-negative $C$ and $p$ such that   
for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have    
$$   
\COMP(\calA(\calC), \varepsilon,R)\le   
C\,\exp\left(p\,(1+\log\,d)(1+\log\,\varepsilon^{-1})\right).   
$$    
The infimum of $p$ satisfying the bound above is denoted by $p^*$   
and is called the exponent of quasi-polynomial tractability.    
\newline \qquad

\item   
We say that the problem is $(s,t)$-weakly tractable for positive $s$ and $t$ iff    
$$   
\lim_{d+\varepsilon^{-1}\to\infty}\   
\frac{\log\, \COMP(\calA(\calC), \varepsilon,R)}   
{d^{\,t}+\varepsilon^{-s}}\,=\,0.   
$$    
\newline \qquad

\item    
We say that the problem is uniformly weakly tractable if and only if it 
is $(s,t)$-weakly tractable for all positive $s$ and $t$.    
\end{itemize}

}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Cone and the Optimal Algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{theorem}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
\begin{equation} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \varepsilon/(\frakC R) \right \}.
\end{equation}
The computational complexity has the lower bound
\begin{equation} \label{DHKM:PilotConeAlg_comp}
        \COMP(\calA(\calC),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
\end{equation}
\end{theorem}

\begin{proof} 
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \},  
\end{align*}
since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le \norm[\calF]{f} \le R$ for all $f \in \calB_R$.  Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.   Fix $R$ and $\varepsilon$ arbitrarily.  Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.  Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.

@@

Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
=\frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
& \ge \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
\end{align*}
by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  This inequality implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tractability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{Next should come tractability}

\PeterNote{It seems to me that we can handle this case by an analogy to tractability for the 
average case setting. There, the complexity also depends on the truncated trace of the eigenvalues.}
\FredNote{Agreed.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Necessary Condition for the Input Function to Lie in the Cone}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{Fred should add about the necessary conditions.}
Although we may not be able to guarantee that the particular $f$ of interest lies in the cone, $\calC$, we may derive necessary conditions for $f \in \calC$.  The following proposition follows from the definition of $\calC$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.

\begin{proposition}
If $f \in \calC$ and $n^*$ is defined as in Algorithm \ref{DHKM:PilotConeAlg}, then 
\begin{equation} \label{DHKM:PilotConeNecessary}
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n^*}} \le \frakC 
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n_1}}.
\end{equation}
\end{proposition}

If it is found in practice that condition \eqref{DHKM:PilotConeNecessary} is violated, then Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.  An alternative is to make the cone more inclusive by increasing $\frakC$ and/or $n_1$.

@@

From the argument leading to \eqref{DHKM:SOL_A} it follows that 
\begin{equation} \label{DHKM:APP_Err_Coef}
    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
\end{equation}
Thus, the faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.  A disadvantage of Algorithm \ref{DHKM:PilotConeAlg} is that it cannot adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$. In this section, we develop an algorithm that can do so.

Let $(n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.  This sequence may increase geometrically or algebraically. For any $f \in \calF$, define the partial sums of powers of series coefficients:
\[
\sigma_j (f):=\norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n_{j-1}-1}^{n_j}} \qquad \text{for}\ j \in \N,
\]
We now define the cone of input functions, $\calC$, by
\begin{equation} \label{DHKM:TrackConeDef}
  \calC : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
\end{equation}
Here, $a$ and $b$ are positive reals with $b< 1 < a$. The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$. Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.

From the expression for the error in \label{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound for $j \in \bbN$:
\begin{align}
\nonumber
\norm[\calG]{\SOL(f)-\APP(f,n_j)} &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty} \\
\nonumber 
& = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \abs{\hf(\bsk_i) }^{\tau}  \right\}^{1/\tau} = \norm[\tau]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
&\le \norm[\tau]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
 = \displaystyle a \left(\frac{b^\tau}{1 - b^\tau} \right)^{1/\tau} \sigma_{j}(f)
 \label{DHKM:algoineq}
\end{align}
This upper bound depends only on the function data and the parameters defining $\calC$.  The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.  Moreover, the error of $\APP(f,n_j)$ is asymptotically no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.

\FredNote{Perhaps Yuhan can fill in here following our \cite{DinHic20a} paper.}

\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adaptive Algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{algorithm}
	\caption{Adaptive ALG for a Cone of Input Functions} 
	\begin{algorithmic}
	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0},$ where $j \in \N$ starts from 1;  $\APP$ satisfying \eqref{DHKM:algoineq}
		\INPUT a black-box function, $f$; an absolute error tolerance,
		$\varepsilon>0$

\Ensure  Choose $j^* =  \min \left \{j \in \N : 
\sigma_{j}(f) < \frac{\varepsilon}{a}\left(\frac{1 - b^\tau}{b^\tau} \right)^{1/\tau} 
\right \}$

\RETURN $\ALG(f,\varepsilon) = \APP(f,j^*)$
\end{algorithmic}
\end{algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inferring Coordinate Importance and Smoothness} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{The work with Simon}

\begin{acknowledgement}
 P.~Kritzer gratefully acknowledges support by the Austrian Science Fund (FWF) Project  F5506-N26, 
which is part of the Special Research Program ``Quasi-Monte Carlo Methods: Theory and Applications''.
\end{acknowledgement}
